% Copyright (C) 2022 CDN (Diego) Damasceno
\documentclass[11pt,a4paper]{article}

\usepackage[english]{babel}
\usepackage{inputenc}
\usepackage[T1]{fontenc}
\usepackage{currvita}
\usepackage[square,sort,comma,numbers]{natbib}
\bibliographystyle{acm}
\usepackage{bibentry}
\usepackage{xcolor}
\usepackage[colorlinks = true,
            linkcolor = blue,
            urlcolor  = blue,
            citecolor = blue,
            anchorcolor = blue]{hyperref}
\usepackage{enumitem}

\definecolor{darkblue}{HTML}{1F4788}
\definecolor{lightgray}{HTML}{4A4A4A}
% \usepackage[margin=2.0cm]{geometry}
\usepackage[left=2cm,right=2cm,top=2cm,bottom=2cm]{geometry}
% \usepackage[bottom=2.5cm,top=2.5cm]{geometry}

\usepackage{titlesec}

% Conditional printing 
\newif\ifREFs% \REFsfalse (List of References)
\newif\ifPersonalInfo % \PersonalInfofalse (Personal information)

\PersonalInfotrue % Prints phone, gmail/skype, custom closing message
\REFstrue % Prints references

% Sections formatting
\titleformat{\section}{\scshape\raggedright\large}{}{0em}{}[\color{black}\titlerule]
\titleformat{\subsection}{\bfseries\raggedright\large}{}{0em}{}[]

% Phone and Email as hyperlinks
\usepackage{color}
\newcommand\phone[1]{\href{tel:#1}{{\emailfont #1}}}
\newcommand\email[1]{\href{mailto:#1}{{\emailfont #1}}}
\newcommand\emailfont{\sffamily}

% CV Info (to be customized).
\newcommand{\CVAuthor}{Dr. Valentin Kiefner}
\newcommand{\CVTitle}{V.Kiefner_short_CV}
\newcommand{\CVWebpage}{https://www.wu.ac.at/iib/iib/teams/team-mohr/valentin-kiefner-1/}

\ifPersonalInfo
    \newcommand{\CVNote}{CV compiled on {\today} }
\else
    \newcommand{\CVNote}{CV compiled on {\today} for the website \CVWebpage}
\fi

\begin{document}
\begin{cv}
\begin{center}
{\LARGE\textbf{\color{darkblue}Dr. Valentin Kiefner}}\\[6pt]
{\large \textit{Postdoctoral Researcher}}\\
{\large Vienna University of Economics and Business}\\[12pt]
\end{center}

\section{Personal Information}
  \begin{cvlist}{}
  \item
    Institute for International Business\\
    Department of Global Business \& Trade\\
    Welthandelsplatz 1, 1020\\
    Vienna, Austria

  \item 
    \ifPersonalInfo
        Birth date: 07 March 1994\\
        Place of birth: Hamburg, Germany\\
        Nationality: German\\
    \fi
    \ifPersonalInfo
        Tel.:~\phone{+43~(1)~31336-5771}\\
    \else
        Tel.:~\texttt{Available upon request}\\
    \fi
    Email:~\email{valentin.kiefner@wu.ac.at}\\
    Google Scholar: \href{https://scholar.google.com/citations?user=JwNZJX0AAAAJ&hl=de&oi=ao}{Profile}\\
    ORCiD: \href{https://orcid.org/0009-0008-6763-1065}{0009-0008-6763-1065}\\
    Linkedin: \href{https://linkedin.com/in/valentin-kiefner/}{linkedin.com/in/valentin-kiefner}

  \end{cvlist}
  
% \vspace{-0.75cm}
\section{Academic Positions}
  \begin{cvlist}{}
    \item[09/2020--Current]
      {\textbf{WU Vienna University of Economics \& Business}}\\
      {Position:} Research \& Teaching Associate\\
      {Department:} Department of Global Business \& Trade\\
      {Supervisor:} {Univ.-Prof.Dr. Alexander Mohr}
        
    \item[09/2019--08/2020]
      {\textbf{WU Vienna University of Economics \& Business}}\\
      {Position:} Academic Tutor\\
      {Department:} Department of Global Business \& Trade\\
  \end{cvlist}

\section{International Appointments}
  \begin{cvlist}{}
    \item[08/2022--12/2022]
      {\textbf{Keio University}}\\
      {Position:} Visiting PhD Researcher\\
      {Faculty:} Faculty of Business and Commerce\\
      {Location:} Tokyo, Japan\\
      {Funding:} International Research Fellow Program, WU Vienna\\
      {Supervisor:} Dr. Chie Iguchi
  \end{cvlist}

\section{Education}
  \begin{cvlist}{}
  \item[09/2020--03/2026] 
      \textbf{Doctorate} {{\textbf{Economic \& Social Sciences (with honors)}}}\\ 
      WU University of Economics \& Business, Vienna, Austria\\
      \textbf{Thesis:} {"Corporate Sustainability Action in International Business: Success Factors for Strategic Implementation and Challenges for Operational Realization"}\\
      \textbf{Advisor:} {Univ.-Prof.Dr. Alexander Mohr}\\
      \textbf{Co-Advisor:} {Univ.-Prof.Dr. Jonas Puck}\\
      \textbf{Co-Advisor:} {Prof. Hafiz Mirza}
      
    \item[02/2022--06/2024] 
      \textbf{Micro Master} {{\textbf{Statistics \& Data Science (MITx)}}}\\ 
      MIT’s Institute for Data, Systems, and Society (IDSS), online on eDx
  \item[09/2018--08/2020] 
      \textbf{MSc} {{\textbf{Export \& Internationalization Management (with honors)}}}\\
      WU University of Economics \& Business, Vienna, Austria\\
      \textbf{Thesis:} "Small Firms - Big Cases: SMEs in the Context of International Investment Disputes" \\
      \textbf{Advisor:} {Mag.Dr. Simon Hartmann}
      
  \item[03/2013--03/2017] 
      \textbf{BA} {{\textbf{Corporate Management \& Economics}}}\\
      Zeppelin University, Friedrichshafen, Germany\\
      \textbf{Thesis:} "Establishing Linkages Between Leadership and Emotional Intelligence – The Case of the Narcissistic Leader"\\
      \textbf{Advisor:} {Prof.Dr. Carmen Tanner}
  \end{cvlist}
  
%\vspace{-1cm}
\section{Publications}

\subsection{Journal Publications}
\begin{cvlist}{}
    \item[2022]
      \textbf{Kiefner, V.}, Mohr, A., \& Schumacher, C. (2022). 
      Female executives and multinationals' support of the UN's Sustainable Development Goals. 
      \textit{Journal of World Business}, Vol.{57}(3), DOI: \href{https://www.sciencedirect.com/science/article/pii/S1090951621001152}{10.1016/j.jwb.2021.101304}\\ 
      (4 Journal – AJG 2024) | Citations: $\sim$50 | Media Coverage: 10+ outlets
\end{cvlist}

\subsection{Conference Proceedings}
\begin{cvlist}{}
    \item[2023]
      Tihanyi, C., Mohr, A., Schumacher, C., \& \textbf{Kiefner, V.} (2023). 
      When Does it Pay to Have a Chief Digital Officer? 
      \textit{Best Papers Proceedings / Academy of Management}, DOI: \href{https://journals.aom.org/doi/abs/10.5465/AMPROC.2023.12432abstract}{10.5465/AMPROC.2023.12432}\\ 
\end{cvlist}

\subsection{Manuscripts in Revision}
\begin{cvlist}{}
    \item[2026]
      \textbf{Kiefner, V.}, Konara, P., Mohr, A., \& Shirodkar, V. (2024). 
      Diversifying for Resilience: How Supply Base International Diversification Relates to Supply Base Sustainability Performance.\\
      \textbf{Outlet:} \textit{Journal of International Business Studies} (4* Journal – AJG 2024) \\
      \textbf{Status:} R\&R Round 3, initiated 06-Mar-2026

    \item[2026]
      \textbf{Kiefner, V.}, Mohr, A., \& Tihanyi, C. (2024). 
      International Diversification and Multinationals' Support of the UN's Sustainable Development Goals: The moderating Role of Digital Technologies. \\
      \textbf{Outlet:} \textit{International Business Review} (3 Journal – AJG 2024) \\
      \textbf{Status:} R\&R Round 3, initiated 03-Mar-2026

    \item[2025]
      Konara, P., Mohr, A., \& \textbf{Kiefner, V.} (2023). 
      The contingent effect of supply base complexity on firm performance: The moderating role of the Covid-19 pandemic.\\
      \textbf{Outlet:} \textit{Journal of Operations Management} (4* Journal – AJG 2024) \\
      \textbf{Status:} R\&R Round 1, initiated 03-Mar-2025 (additional data collection in-process)
\end{cvlist}
 
\subsection{Working Papers}
\begin{cvlist}{}
    \item[In Preparation]
      \textbf{Kiefner, V.}, Stahl, G., \& Schumacher, C. (2026). 
      When Backlash Meets Corporate Climate Action: Societal Polarization and the Relationship Between Top Management Team Diversity and Emissions Reduction in Multinationals.\\
      \textbf{Outlet:} \textit{Strategic Management Journal}\\
\end{cvlist}

\subsection{Policy/Public Engagement}
\begin{cvlist}{}
    \item[2022]
      \textbf{Kiefner, V.} (2022). Women Leaders Increase Company Action on the SDGs. \textit{Network for Business Sustainability}. \href{https://nbs.net/women-leaders-increase-company-action-on-the-sdgs/}{Available Online}\\
\end{cvlist}

\section{Invited Academic Conferences}
 
\begin{cvlist}{}
    \item[2025]
    \textbf{AIB USNE 2025 Conference}: Global Business in a Time of Geopolitical Uncertainty. Bryant University, Rhode Island, USA. \textit{Academy of International Business US Northeast Chapter}
    
    \item[2024]
    \textbf{50\textsuperscript{th} EIBA Anniversary Conference 2024}: JIBS Paper Development Workshop. Aalto University, Helsinki, Finland. \textit{European International Business Academy}
    
    \item[2024]
    \textbf{AIB Annual Conference}: The Dynamics of International Business. Kyung Hee University, Seoul, South Korea. \textit{Academy of International Business}
    
    \item[2023]
    \textbf{EURAM Annual Conference}: Transforming Business for Good. Trinity College, Dublin, Ireland. \textit{European Academy of Management}
    
    \item[2022]
    \textbf{38\textsuperscript{th} EAMSA Annual Conference}: Achieving the Sustainable Development Goals: Prospects and Implications for Euro-Asia Business. Keio University, Tokyo, Japan. \textit{Euro-Asia Management Studies Association}
    
    \item[2022]
    \textbf{11\textsuperscript{th} EIASM Workshop on TMTs}: Strategic Leadership for Sustainability and Social and Political Responsibility. École des Hautes Études Commerciales (HEC), Paris, France. \textit{European Institute for Advanced Studies in Management}
    
    \item[2021]
    \textbf{47\textsuperscript{th} EIBA Annual Conference 2021}: Firms, Innovation and Location: Reshaping International Business for Sustainable Development in the Post-Pandemic Era. Universidad Complutense, Madrid, Spain. \textit{European International Business Academy}
\end{cvlist}


\section{Awards, Research Grants, and Scholarships}
\begin{cvlist}{}
  \item[finalist] Palgrave McMillan EAMSA Best Paper Award (2022)
  \item[EUR 1000] Top-Publication Premium (2022), WU Vienna, Austria 
  \item[EUR 2300] International Research Fellow Program (2022), WU Vienna, Austria
  \item[EUR 8000] Small Project Funding for Junior Researchers (2021/2022), B\&C Private Foundation, Bank Austria
  \item[EUR 1000] Merit-based Scholarship Grant (2020), WU Vienna, Austria
\end{cvlist}

\section{Teaching Experience}

\begin{table}[!ht]
\centering
\begin{tabular}{l|c|c|c|c}
\hline
Course Type & Total Courses & Distinct Courses & Total Enrollments & Total ECTS \\ \hline
Graduate-Level & 6 & 14 & $\sim$880 & 42 \\ 
Undergraduate-Level  & 3 & 3 & $\sim$90 & 68 \\ 
International Programs & 3 & 6 & $\sim$210 & 15 \\ \hline
\textbf{Total} & \textbf{12} & \textbf{23} & \textbf{$\sim$1180} & \textbf{125} \\ \hline
\end{tabular}
\caption{Teaching experience overview by course type}
\end{table}

\subsection{Graduate-Level Courses}
\begin{enumerate}
    \item \textbf{Research Design} (Summer 2026). MSc Export \& Internationalization Management, WU Vienna, Austria. Co-instructor. $\sim$30 students. 5 ECTS. Programme course.
    \item \textbf{Models of Internationalization} (Winter 2021--2024). MSc Export \& Internationalization Management, WU Vienna, Austria. Co-instructor. $\sim$120 students. 5 ECTS. Programme course.
    \item \textbf{Master Thesis Coaching} (Summer 2021--2024). MSc Export \& Internationalization Management, WU Vienna, Austria. Thesis coach/Co-instructor. $\sim$20 students. 2 ECTS. Programme course.
    \item \textbf{Export Management} (Winter 2022/2023). MSc Export \& Internationalization Management, WU Vienna, Austria. Co-instructor. $\sim$120 students. 7.5 ECTS. Programme course.
    \item \textbf{SME Management} (Winter 2021/2022). MSc Export \& Internationalization Management, WU Vienna, Austria. Co-instructor. $\sim$120 students. 7.5 ECTS. Programme course.
    \item \textbf{Research Design / Literature Seminar} (Summer 2021/2022). MSc Export \& Internationalization Management, WU Vienna, Austria. Co-instructor. $\sim$30 students. 5 ECTS. Programme course.
\end{enumerate}
 
\subsection{Undergraduate-Level Courses}
\begin{enumerate}
    \item \textbf{International Business Applications} (Summer 2025). BSc International Business, WU Vienna, Austria. Course leader. $\sim$30 students. 5 ECTS. Specialization course.
    \item \textbf{Global Strategy and International Alliances} (Summer 2025). BSc International Business, WU Vienna, Austria. Co-instructor. $\sim$30 students. 5 ECTS. Specialization course.
    \item \textbf{International Business Strategy} (Summer 2025). International programmes (international students), WU Vienna, Austria. Co-instructor. $\sim$30 students. 5 ECTS. Course offering for international students.
\end{enumerate}

\subsection{International Programs \& Summer Schools}
\begin{enumerate}
    \item \textbf{International Summer University: Strategy Meets Finance} (Summer 2025). WU Vienna, Austria. Co-instructor. $\sim$30 students. 5 ECTS. Two-week intensive programme for incoming international students (co-taught with PD Dr.~Jakob Müllner).
    \item \textbf{Bangkok Summer School on International Business \& Sustainable Development} (Summer 2022--2025). Mahidol University -- CMMU (Thailand). Co-developer \& instructor. $\sim$40 students. 8 ECTS. Three-week intensive programme on global value chains, corporate sustainability, and UNSDGs.
    \item \textbf{Erasmus+ International Short Program} (Summer 2023). University of Sarajevo, Bosnia and Herzegovina. Instructor/Co-developer. $\sim$20 students. 2 ECTS.Intensive programme on Entrepreneurship and Sustainable Development in International Business (funded by European Commission).
\end{enumerate}

\section{Thesis Supervision}

\subsection{Master Level Theses (Co-supervisor)}

\begin{enumerate}
    \item \textbf{Emanuel Frank} (2024, completed). Sustainability Implementation in Logistics Companies: The Influencing Role of the Insurance Sector. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC17088491}
    
    \item \textbf{Maximilian Müller-Guttenbrunn} (2023, completed). Measures to Increase Electronic Waste Collection Rates: An Integrative Literature Review. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC17010455}
    
    \item \textbf{Marcel Krainz} (2023, completed). Does Sustainability Increase Firm Performance? A Panel Data Analysis During the COVID-19 Pandemic. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC17083758}
    
    \item \textbf{Luca Anton Christandl} (2023, completed). Circular Economy: Development of a Holistic Model for Circular Transition in the Manufacturing Industry. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC17026452}
    
    \item \textbf{Theresa Hirsch} (2023, completed). Success Factors for Cybersecurity Adoption in Austrian SMEs: Assessing the Threat Landscape and Developing a Framework Applicable for SMEs. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC17022329}
    
    \item \textbf{Belinda Beimrohr} (2023, completed). Empowering Environmental Sustainability in the Austrian Hotel Industry: Identifying Drivers for Sustainable Energy Measures. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC17025457}
    
    \item \textbf{Mariam Rashwan} (2023, completed). Pathways to Achieving the UN Sustainable Development Goals: The Role of Multinational Enterprises in Austria and Digitalization Measures for SDG Implementation. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC16984544}
    
    \item \textbf{Philipp Wersch} (2022, completed). Challenges When Monitoring Sub-suppliers with Regards to Environmental Sustainability. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC16698539}
    
    \item \textbf{Bettina Stöllinger} (2022, completed). Benefits of Being Part of the Solution: Sustainable Development Goals as a Promoter of Dynamic Green Capabilities. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC16706131}
    
    \item \textbf{Bernhard Wieseneder} (2022, completed). Corporate Sustainability Disclosure of Austrian Listed Companies: A Systematic Content Analysis. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC16693373}
    
    \item \textbf{Charlott Sophie Mahler} (2022, completed). Global Cities: Location Choice and Performance Outcomes. Is There a Zone of Optimal Performance for Foreign Subsidiaries in Vienna? WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC16713128}
    
    \item \textbf{Stella Henriette Pohlner} (2022, completed). Sustainability in Automotive First-tier Supply Chains: How Can Automotive Focal Firms Implement Their Sustainability Standards into Their First-tier Supplier Relationships? WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC16734910}
    
    \item \textbf{Doris Vindl} (2022, completed). Institutional Factors and Environmental Disclosure: An Emerging Market Perspective. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC16678927}
    
    \item \textbf{Angelo Eder} (2021, completed). The Influence of Digitalization on SME Firm Performance During the COVID-19 Pandemic: A Qualitative Case Study. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC16664543}
    
    \item \textbf{Rico Schöffmann} (2021, completed). Implementation of Codes of Conduct Guidelines Across Global Supply Chains: A Literature Review on Sustainable Supply Chain Management in International Business Research. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC16421544}
    
    \item \textbf{Melanie Sochatzy} (2021, completed). Sustainable Supply Chain Management in Multinational Enterprises and the Effect of Stakeholder Pressure: A Cross-Industry Multiple Case Study. WU Vienna, Austria. \url{https://permalink.obvsg.at/wuw/AC16404566}
\end{enumerate}

\subsection{Bachelor Level Theses (Co-supervisor)}

\begin{enumerate}
    \item \textbf{Julia Leitner} (2021, completed). A Systematic Literature Review on the Global Dimension of Corporate Sustainability in International Business (IB) Research. WU Vienna, Austria.
\end{enumerate}


\section{Schools and Workshops Attended}
\begin{cvlist}{}
    \item[{Feb 2026}] Artificial Intelligence and Large Language Models for Social Scientist. \textit{WU Vienna University}, AT
    \item[{Jan 2026}] Reproducible Research with Python. \textit{WU Vienna University}, AT
    \item[{Mar 2022}] Applied Quantitative Methods. \textit{Copenhagen Business School}, DK
    \item[{Nov 2020}] Theory of the MNE \& Economics of IB. \textit{Henley Business School, University of Reading}, UK
\end{cvlist}

\section{Community Services}
\subsection{Department Conference}
\begin{cvlist}{}
\item \begin{enumerate}[leftmargin=-2cm]
        \item \textit{Elected Junior Faculty Representative} {(2026)}: Department of Global Business \& Trade
        \item \textit{Elected Junior Faculty Representative} {(2025)}: Department of Global Business \& Trade
    \end{enumerate}
\end{cvlist}

%   \vspace{-1cm}
\section{Languages}
German (native -- speaking, reading, writing); English (fluent -- speaking, reading, writing); French (Baccalauréat général); Latin (Great Latinum)

\section{Personal Interests}
Triathlon (Ironman finisher 2024/2025), trail running (ultramarathon), friends and good discussions, mountaineering and snowboarding (often Alps), passionate cook, interested in classical music, literature, and cinema.

% \vspace{1cm}

\ifREFs% \ALLfalse
\section{References}
  \begin{cvlist}{}
  \item[\textbf{Prof. Dr. Günter K. Stahl}] (Mentor)
  \item[~ ~{Position:}]  Professor at Vienna University of Economics \& Business 
  \item[~ ~{Institute:}]  Institute for Responsibility and Sustainability in Global Business (RSGBI)
  \item[~ ~{Address:}]   Welthandelsplatz 1, 1020 Vienna, Austria
  \item[~ ~{Email:}]     \href{mailto:guenter.stahl@wu.ac.at}{guenter.stahl@wu.ac.at}
  \item[\textbf{Prof. Dr. Jonas Puck}]  (Ph.D. Co-Advisor)
  \item[~ ~{Position:}]  Professor at Vienna University of Economics \& Business 
  \item[~ ~{Department:}] Institute of International Business (IIB)
  \item[~ ~{Address:}]   Welthandelsplatz 1, 1020 Vienna, Austria
  \item[~ ~{Email:}]     \href{mailto:jonas.puck@wu.ac.at}{jonas.puck@wu.ac.at}
  \end{cvlist}
\fi

\vfill
  \hfill\cvplace{Vienna - Austria}
\end{cv}
\end{document}
\endinput
%%
